---
title: "Article Analysis: ENVS 4826 Assignment 2"
author: "Pavlos Skarvelis"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## 1.Introduction

This paper is intended as a summary and analysis of the article *Ageing Research Reviews* by Mark, et al., 2016. Discussed below will be the methodology of how research was conducted, along with any findings that were prevalent in the research discussed. Through the following summary, I hope to encourage many of my peers to experiment with intermittent fasting on an annually or bi-annually basis.

## 2.Methods

The authors of the article pulled much of their source information from other articles that have produced controlled lab tests and field studies. In depth summary of controlled groups was presented prior to showing concluding evidence, as seen in section 2. *IF and health indicators in Laboratory animals*. The article covered many ranges of human and animal health-related risks that intermittent fasting impacts. Examples of intermittent fasting within humans was also displayed. Ghandi was used in explaining the nuerological benefits of intermittent fasting exhibited in him. 

## 3.Results

Mark, et al., resulted that intermittent fasting conducted properly in periods of alternate day fasting, resulted in increased brain function and activity in both animal and human studies. Many of the health stressor of mid to late aged individuals were decreased by intermittent fasting, in particular, individuals with neuronal dysfunction, Alzheimers and Parkinson's disease were studied to have fewer memory lapses and increased motor functions. 

## Figures 

![*Figure 1*. The above represents three different eating habits and how the gluecose intake affects the ketones levels in individuals livers. Keytone levels are imperative to transforming fatty lipids into energy, thus "burning" fat in an individuals body. A constant supply of gluecose, as seen in A, exhibits no ketone production within the liver, continuing the cycle of fat collection, whilst B and B have 24 and 18 hour intervals, stimulating the production of ketones.](https://ars.els-cdn.com/content/image/1-s2.0-S1568163716302513-gr1_lrg.jpg) 

```{r pressure, echo=FALSE}
plot(pressure)
```

